Andres Karjus

### 2018-11-06 index.Rmd
preprint link

* [Slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) of the talk _Challenges in detecting evolutionary forces in language change using diachronic corpora_ presented at the [CLE](http://www.lel.ed.ac.uk/cle/) seminar series, 06.11.2018 | preprint (pending) | [code](https://github.com/andreskarjus/wfsim_fit)

@@

* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, Challenges in detecting evolutionary forces in language change using diachronic corpora | arXiv preprint | [code](https://github.com/andreskarjus/wfsim_fit) 
* Andres Karjus, Martin Ehala, 2018. Testing an agent based model of language choice on sociolinguistic survey data. Language Dynamics and Change, 8, pp. 219-252 | [Online at Brill](https://doi.org/10.1163/22105832-00802004) | [postprint](Karjus_Ehala_2018_Testing_an_agent-based_model_of_language_choice_LDCpostprint.pdf) | <a href="karjus_testing_2018.bib" target="_blank">bib</a> | sociolinguistic [dataset](http://doi.org/10.15155/1-00-0000-0000-0000-00162L): 1000 respondents, 200 questions
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018 [to appear in Language Dynamics and Change]. Quantifying the dynamics of topical fluctuations in language. | [arXiv preprint](https://arxiv.org/abs/1806.00699) | <a href="karjus_quantifying_2018.bib" target="_blank">bib</a> | [code](https://github.com/andreskarjus/topical_cultural_advection_model) | recipient of the Edinburgh PPLS [Gray postgraduate publication prize](https://www.ed.ac.uk/ppls/philosophy/current/postgraduate/fees-and-funding/ppls-gray-postgraduate-publication-prize)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Topical advection as a baseline model for diachronic lexical dynamics. Proceedings of The Society for Computation in Linguistics. Volume 1. [extended abstract, full paper above] | [open access](http://scholarworks.umass.edu/scil/) | <a href="karjus_topical_2018.bib" target="_blank">bib</a>
*	Martin Haspelmath, Andres Karjus, 2017. Explaining asymmetries in number marking: Singulatives, pluratives and usage frequency. Linguistics, volume 55, issue 6. | [online version](https://www.degruyter.com/view/j/ling.2017.55.issue-6/ling-2017-0026/ling-2017-0026.xml)  | [preprint](https://www.academia.edu/25032500/Explaining_asymmetries_in_number_marking_Singulatives_pluratives_and_usage_frequency) | <a href="haspelmath_explaining_2017.bib" target="_blank">bib</a>
*	Andres Karjus, 2015. Through the Spyglass of Synchrony: Grammaticalization of the Exterior Space in the Eastern Circum-Baltic. In: Hilpert, Martin, Östman, Jan-Ola, Mertzlufft, Christine, Rießler, Michael, Duke, Janet (eds.), Advances in Nordic Linguistics. De Gruyter Mouton.
| [google books](https://books.google.ee/books?id=BPheCAAAQBAJ)
*	Andres Karjus (editor), 2013. Areal linguistics, Grammar and Contacts. Special issue of the Journal of Estonian and Finno-Ugric Linguistics, 4-2. Tartu: University of Tartu Press. 
| [open access](http://jeful.ut.ee/index.php/JEFUL/issue/view/2013.4.2)
* Petar Kehayov, Eva Saar, Miina Norvik, Andres Karjus, 2013. Hääbuva kesklüüdi murde jälgedel suvel 2012 [On the footsteps of vanishing Central Lude in the summer of 2012]. Yearbook of the Estonian Mother Tongue Society, Vol. 58. | [open access](http://www.kirj.ee/public/ESA/2012/esa_58-2012-58-101.indd.pdf)
*	Andres Karjus, 2012. Outdoors on the Shores of the Baltic: Gradience in the Grammaticalization of the Exterior-Region. Journal of Estonian and Finno-Ugric Linguistics 3-1, pp. 209-226.

@@

- [The inaugural meeting of the Society for Computation in Linguistics](https://blogs.umass.edu/scil/scil-2018/), part of [LSA 2018](https://www.linguisticsociety.org/event/lsa-2018-annual-meeting) | download [poster](scilposter_sizeA1.pdf)
- [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/)
- [Evolang 2018](http://evolang.cles.umk.pl) | [slides](https://drive.google.com/open?id=10az7BOV_tT-mAwMZXDoguKmZeTErnfzB) | [open-access proceedings](http://evolang.org/torun/proceedings/papertemplate.html?p=117) 
- [Applications in Cultural Evolution: Arts, Languages, Technologies](https://cultevol.ut.ee/) | _Selection above the baseline: quantifying the advection effect in four domains of cumulative culture_ | [slides](https://andreskarjus.github.io/cultevol_tartu_slides) with interactive data&plots | [code](https://github.com/andreskarjus/cultural_advection_Tartuce)
- New directions in language evolution research workshop, at the [SLE 2018](http://sle2018.eu/) | _Two problems and solutions in evolutionary corpus-based language dynamics research_ [slides](https://andreskarjus.github.io/sle_tallinn_languagedynamics) with interactive plots | [code](https://github.com/andreskarjus/sle_tallinn_languagedynamics)
- University of Edinburgh Centre for Language Evolution seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)

>>>>

* [Slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) of the talk _Challenges in detecting evolutionary forces in language change using diachronic corpora_ presented at the [CLE](http://www.lel.ed.ac.uk/cle/) seminar series, 06.11.2018 | paper preprint now also on [arXiv](http://arxiv.org/abs/1811.01275) | [code](https://github.com/andreskarjus/wfsim_fit)

@@

* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith 2018. Challenges in detecting evolutionary forces in language change using diachronic corpora | [arXiv preprint](http://arxiv.org/abs/1811.01275) | [code](https://github.com/andreskarjus/wfsim_fit) 
* Andres Karjus, Martin Ehala, 2018. Testing an agent based model of language choice on sociolinguistic survey data. Language Dynamics and Change, 8, pp. 219-252 | [Online at Brill](https://doi.org/10.1163/22105832-00802004) | [postprint](Karjus_Ehala_2018_Testing_an_agent-based_model_of_language_choice_LDCpostprint.pdf) | <a href="karjus_testing_2018.bib" target="_blank">bib</a> | sociolinguistic [dataset](http://doi.org/10.15155/1-00-0000-0000-0000-00162L): 1000 respondents, 200 questions
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Quantifying the dynamics of topical fluctuations in language. | [arXiv preprint](https://arxiv.org/abs/1806.00699) | <a href="karjus_quantifying_2018.bib" target="_blank">bib</a> | [code](https://github.com/andreskarjus/topical_cultural_advection_model) | recipient of the Edinburgh PPLS [Gray postgraduate publication prize](https://www.ed.ac.uk/ppls/philosophy/current/postgraduate/fees-and-funding/ppls-gray-postgraduate-publication-prize)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Topical advection as a baseline model for diachronic lexical dynamics. Proceedings of The Society for Computation in Linguistics. Volume 1. [extended abstract, full paper above] | [open access](http://scholarworks.umass.edu/scil/) | <a href="karjus_topical_2018.bib" target="_blank">bib</a>
*	Martin Haspelmath, Andres Karjus, 2017. Explaining asymmetries in number marking: Singulatives, pluratives and usage frequency. Linguistics, volume 55, issue 6. | [online version](https://www.degruyter.com/view/j/ling.2017.55.issue-6/ling-2017-0026/ling-2017-0026.xml)  | [preprint](https://www.academia.edu/25032500/Explaining_asymmetries_in_number_marking_Singulatives_pluratives_and_usage_frequency) | <a href="haspelmath_explaining_2017.bib" target="_blank">bib</a>
*	Andres Karjus, 2015. Through the Spyglass of Synchrony: Grammaticalization of the Exterior Space in the Eastern Circum-Baltic. In: Hilpert, Martin, Östman, Jan-Ola, Mertzlufft, Christine, Rießler, Michael, Duke, Janet (eds.), Advances in Nordic Linguistics. De Gruyter Mouton.
| [google books](https://books.google.ee/books?id=BPheCAAAQBAJ)
*	Andres Karjus (editor), 2013. Areal linguistics, Grammar and Contacts. Special issue of the Journal of Estonian and Finno-Ugric Linguistics, 4-2. Tartu: University of Tartu Press. 
| [open access](http://jeful.ut.ee/index.php/JEFUL/issue/view/2013.4.2)
* Petar Kehayov, Eva Saar, Miina Norvik, Andres Karjus, 2013. Hääbuva kesklüüdi murde jälgedel suvel 2012 [On the footsteps of vanishing Central Lude in the summer of 2012]. Yearbook of the Estonian Mother Tongue Society, Vol. 58. | [open access](http://www.kirj.ee/public/ESA/2012/esa_58-2012-58-101.indd.pdf)
*	Andres Karjus, 2012. Outdoors on the Shores of the Baltic: Gradience in the Grammaticalization of the Exterior-Region. Journal of Estonian and Finno-Ugric Linguistics 3-1, pp. 209-226.

@@

- The inaugural meeting of the Society for Computation in Linguistics, part of [LSA 2018](https://www.linguisticsociety.org/event/lsa-2018-annual-meeting) | download [poster](scilposter_sizeA1.pdf)
- [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/)
- [Evolang 2018](http://evolang.cles.umk.pl) | [slides](https://drive.google.com/open?id=10az7BOV_tT-mAwMZXDoguKmZeTErnfzB) | open-access [proceedings](http://evolang.org/torun/proceedings/papertemplate.html?p=117) 
- [Applications in Cultural Evolution: Arts, Languages, Technologies](https://cultevol.ut.ee/) | _Selection above the baseline: quantifying the advection effect in four domains of cumulative culture_ | [slides](https://andreskarjus.github.io/cultevol_tartu_slides) with interactive data&plots | [code](https://github.com/andreskarjus/cultural_advection_Tartuce)
- New directions in language evolution research workshop, at the [SLE 2018](http://sle2018.eu/) | _Two problems and solutions in evolutionary corpus-based language dynamics research_ [slides](https://andreskarjus.github.io/sle_tallinn_languagedynamics) with interactive plots | [code](https://github.com/andreskarjus/sle_tallinn_languagedynamics)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)
